\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Font options
\usepackage[sfdefault]{roboto}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{\Large\bfseries\scshape\raggedright}{}{0em}{}[\titrule]

% Ensure PDF is machine readable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubheading}[4]{
\vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4} \\
  \end{tabular*}\vspace{-7pt}
}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingList}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

\begin{center}
  \textbf{\Huge Roopa Saira Thomas} \\
  \small 347-216-6462 $|$ \href{mailto:roopasairathomas@gmail.com}{roopasairathomas@gmail.com} $|$ 
  \href{https://linkedin.com/in/roopa-saira-thomas}{linkedin.com/in/roopa-saira-thomas}
\end{center}

\section*{Professional Summary}
Analytical Structural Engineer moving into AI Automation and Agentic Workflow Development. Specialized in architecting Self-Healing Compliance Engines and Multimodal RAG agents using n8n, Mistral-Large, and Vector Databases. Applies structural design logic to digital automation, optimizing complex regulatory requirements and unstructured data for improved business outcomes.

\section{Technical Skills}
\resumeSubHeadingList
  \resumeItem{\textbf{AI and No-Code Tools}: n8n, Mistral-Large, multimodal RAG, Pinecone, PG Vector}
  \resumeItem{\textbf{Automation}: Selenium}
  \resumeItem{\textbf{Engineering Software}: AutoCAD, Staad Pro, ANSYS, Solid Edge, Quadra}
  \resumeItem{\textbf{Core Competencies}: Workflow architecture, technical documentation, data normalization, project management}
\resumeSubHeadingListEnd

\section{Ai And Automation Projects}
\resumeSubHeadingList
  \resumeSubheading
      {Agentic Self-Healing Compliance System (SEC/FINRA 2026)}{2026}
      {Automation Architect}{n8n, Mistral-Large}
      \resumeSubHeadingList
          \resumeItem{Architected an automated regulatory remediation system using n8n and Mistral-Large to meet 2026 SEC/FINRA standards.}
          \resumeItem{Developed a JavaScript Validation Layer that autonomously detects compliance gaps and triggers "self-healing" loops to correct data before final submission.}
          \resumeItem{Integrated Vector RAG to allow the agent to cross-reference internal documents against real-time regulatory databases.}
      \resumeSubHeadingListEnd

  \resumeSubheading
      {Legal-AI: Automated Contract Triage (HITL)}{2025}
      {Workflow Developer}{n8n, HITL}
      \resumeSubHeadingList
          \resumeItem{Engineered a Human-in-the-Loop (HITL) system to classify and risk-score legal contracts.}
          \resumeItem{Utilized n8n to automate the extraction of high-risk clauses, reducing manual review time for legal teams.}
      \resumeSubHeadingListEnd

  \resumeSubheading
      {Enterprise Insurance Document Intelligence Agent}{2025}
      {RAG Specialist}{Pinecone, Multimodal RAG}
      \resumeSubHeadingList
          \resumeItem{Built a multimodal RAG system to process and query insurance PDFs and images.}
          \resumeItem{Implemented vector storage with Pinecone for high-precision data retrieval, significantly reducing policy review time.}
      \resumeSubHeadingListEnd

  \resumeSubheading
      {Automated Document Management Ecosystem}{2025}
      {Automation Lead}{n8n, Google Drive API}
      \resumeSubHeadingList
          \resumeItem{Developed an end-to-end n8n workflow that detects embedded images in emails and automatically routes them to dynamically created folders in Google Drive.}
          \resumeItem{Eliminated manual data entry by automating file naming conventions and directory structures.}
      \resumeSubHeadingListEnd
\resumeSubHeadingListEnd

\section{Professional Experience}
\resumeSubHeadingList
  \resumeSubheading
      {Independent Technical Consultant}{Jan 2018 -- Jan 2021}
      {Technical Consultant}{Technical Design \& Supervision}
      \resumeSubHeadingList
          \resumeItem{Led technical design reviews and structural assessments for significant church renovation.}
          \resumeItem{Collaborated with construction firm on site supervision throughout project transitions.}
          \resumeItem{Produced detailed technical documentation to ensure clarity and consistency in execution.}
      \resumeSubHeadingListEnd

  \resumeSubheading
      {BTC College of Engineering and Technology}{Aug 2017 -- July 2018}
      {Assistant Professor}{Academic Quality Assurance}
      \resumeSubHeadingList
          \resumeItem{Instructed courses in Geotechnical Engineering and Fluid Mechanics.}
          \resumeItem{Managed Staad Pro Lab and led departmental internal monitoring for academic quality assurance and served as Class Tutor for engineering cohorts.}
      \resumeSubHeadingListEnd

  \resumeSubheading
      {Skyline Builders}{Aug 2016 -- May 2017}
      {Trainee Engineer}{Conformity \& Estimates}
      \resumeSubHeadingList
          \resumeItem{Produced client drawings, extra work estimates and handled municipal/fire department conformity approvals.}
          \resumeItem{Ensured drawings met strict conformity and accuracy standards for municipalities and fire departments.}
      \resumeSubHeadingListEnd
\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingList
  \resumeSubheading
      {JCT College of Engineering And Technology (Anna University)}{}
      {Master of Engineering (M.E.) Structural Engineering | GPA: 77\%}{}
  \resumeSubheading
      {Vivekanandha College of Technology (Anna University)}{}
      {Bachelor of Engineering (B.E.) Civil Engineering | GPA: 78\%}{}
\resumeSubHeadingListEnd

\section{Publications, Training \& Languages}
\resumeSubHeadingList
  \resumeItem{\textbf{Publications}: Concrete Replacement with GGBS and Rice Husk Ash (IJSR); Stabilization of Expansive Soil using Fly ash (IJRCE)}
  \resumeItem{\textbf{Training}: FEA of Building Structures using ANSYS}
  \resumeItem{\textbf{Languages}: English, Hindi, Tamil, French, Malayalam}
\resumeSubHeadingListEnd

\section{References}
\resumeSubHeadingList
  \resumeItem{\textbf{Mr. Gnanraj Devadoss}, Asst.Engineer, Mettur Thermal Power Station, +91 9894200772}
  \resumeItem{\textbf{Dr. Abilash K.S}, Former Principal, BTC College, Koothattukulam, Kerala, +91 7907105628}
\resumeSubHeadingListEnd

\end{document}